Interval Probability for Fuzzy Quantum Theories

### 2016-07-29 prob.tex
prob.tex \subsection{Interval-valued probability measures} Updated...

In particular, Dempster-Shafer probability measures are all convex
and have nonempty cores. Need to verify whether general interval-valued
probability measures must have a core or find a counterexample.}

>>>>

In particular, Dempster-Shafer probability measures are all convex
and have nonempty cores.

It seems general interval-valued probability measures must have a
core. Following are proving plan:

\begin{thm}[Neumaier~\cite{Neumaier2003}] For every cloud $\mathbf{x}$
over $\mathbb{M}$ there exists a random variable $x$ with values
in $\mathbb{M}$ contained in $\mathbf{x}$.\qed\end{thm}

\begin{example}[A cloud defines an $R$-probability field~\cite{Lodwick2008}]
...\qed\end{example}

Next need to verify every interval-valued probability measures must
define a cloud...}
